---
title: "p8105 final shiny"
output: 
  flexdashboard::flex_dashboard:
    orientation: row
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(janitor)
library(plotly)
library(stringr)
library(shiny)
library(forcats)
library(shinythemes)

final.dat = read_csv("../data/final_dat.csv") 

ax <- list(
  title = "",
  zeroline = FALSE,
  showline = FALSE,
  showticklabels = FALSE,
  showgrid = FALSE
)



```

Sidebar {.sidebar}
================================================

In this Shiny, we would like to recommend fittest restaurants for customers to satisfy their demand. The data come from [Yelp](https://drive.google.com/drive/folders/190oLdoSyZVnydl9Jxth8G7aKzu3bDgee?usp=sharing).

```{r}
category = final.dat %>% distinct(category) %>% pull()

# selectInput widget for category
selectInput("category_choice", label = h3("Select category"),
            choices = category, selected = "American (Traditional)")


day = final.dat %>% distinct(days) %>% pull()
# selectInput widget for days
selectInput("day_choice", label = h3("Select day"),
            choices = day, selected = "Monday")


max_open = 23
min_open = 0
# sliderInput widget for opening hours
sliderInput("open_range", label = h3("Choose open hour range"),
            min = min_open, max = max_open, value = c(0, 23))

max_close = 23
min_close = 0
# sliderInput widget for opening hours
sliderInput("close_range", label = h3("Choose close hour range"),
            min = min_close, max = max_close, value = c(0, 23))


max_rev = 3000
min_rev = 0
# sliderInput widget for review count
sliderInput("review_num", label = h3("Choose the range of number of reviews"),
            min = min_rev, max = max_rev, value = c(0, 3000))


max_star = 5
min_star = 0
# sliderInput widget for stars
sliderInput("star", label = h3("Choose the range of stars"),
            min = min_star, max = max_star, value = c(0, 5))



# checkboxGroup widget for priceRange
checkboxGroupInput("price_range", label = h3("Choose the price range"), 
    choices = list("$" = 1, "$$" = 2, "$$$" = 3,"$$$$" = 4),
    selected = 1)
```

 Map of restaurants in AZ
==================================================

### Map of restaurants in AZ

```{r}

renderPlotly({
  final.dat %>%
    mutate(text_label = str_c('Name:',name,"\nPostal code: ", postal_code, '\nAddress: ', address, '\nCategory: ', category)) %>% 
    filter(category == input$category_choice,
           stars %in% input$star[1]:input$star[2],
           review_count %in% input$review_num[1]:input$review_num[2],
           RestaurantsPriceRange2 %in% input$price_range,
           days == input$day_choice,
           open %in% input$open_range[1]:input$open_range[2],
           close %in% input$close_range[1]:input$close_range[2]
           ) %>%
    plot_ly(x = ~longitude, y = ~latitude, type = "scatter", mode = "markers",
          alpha = 0.5, 
          color = ~category,
          text = ~text_label)
})

```

Distribution of number of reviews in different categories{.tabset .tabset-fade}
=========================================

###Distribution of number of reviews in different categories

```{r}
renderPlotly({
final.dat %>% 
  group_by(category) %>%
   mutate(median_review = median(review_count)) %>%
   ungroup()%>%
   mutate(category = fct_reorder(category, median_review)) %>% 
  filter(
           stars %in% input$star[1]:input$star[2],
           review_count %in% input$review_num[1]:input$review_num[2],
           RestaurantsPriceRange2 %in% input$price_range
           ) %>%
  plot_ly(y = ~review_count, color = ~category, type = "box",
          colors = "Set2") %>%
  layout(xaxis = ax) 
  
})

```


Mean number of reviews in different categories (in order){.tabset .tabset-fade}
=========================================
Mean number of reviews in different categories (in order)

```{r}
renderPlotly({
final.dat%>% 
group_by(category) %>% 
mutate(mean_review = round(mean(review_count),digits=0)) %>% 
ungroup()%>%
mutate(category = fct_reorder(category, mean_review)) %>%  
filter(
           stars %in% input$star[1]:input$star[2],
           review_count %in% input$review_num[1]:input$review_num[2],
           RestaurantsPriceRange2 %in% input$price_range
           ) %>%
plot_ly(x = ~category, y = ~mean_review, color = ~category, type = "bar")%>%
  layout(xaxis = ax)
  
})

```
